---
title: "Using vetiver on SageMaker with smdocker"
output: html_document
date: '2023-03-03'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Train a model

```{r}
library(tidymodels)
data(bivariate)

biv_rec <-
  recipe(Class ~ ., data = bivariate_train) %>%
  step_BoxCox(all_predictors())%>%
  step_normalize(all_predictors())

svm_spec <-
  svm_linear(mode = "classification") %>%
  set_engine("LiblineaR")

svm_fit <- workflow(biv_rec, svm_spec) %>%
  fit(bivariate_train)

```

## Create a deployable vetiver model

```{r}
library(vetiver)
v <- vetiver_model(svm_fit, "biv-svm")
v
```

## Publish and version model on AWS S3

```{r}
library(pins)
## existing bucket:
identifier <- "sagemaker-vetiver-anthophobic-longhornbeetle"

model_board <- board_s3(bucket = identifier)
vetiver_pin_write(model_board, v)
```

## Build Docker container and deploy endpoint (3 functions):

To create Dockerfile and build:

```{r}
new_image_uri <- vetiver_sm_build(
  board = model_board,
  name = "biv-svm",
  predict_args = list(type = "class", debug = TRUE),
  docker_args = list(base_image = "FROM public.ecr.aws/docker/library/r-base:4.2.2")
)
```

Now set up a model with an endpoint:

```{r}
model_name <- glue::glue("vetiver-sagemaker-{ids::adjective_animal(style = 'kebab')}")

model_name <- 
  vetiver_sm_model(
    new_image_uri,
    model_name,
    tags = list("my-tag" = "support-vector-machine")
  )

new_endpoint <- 
  vetiver_sm_endpoint(
    model_name,
    instance_type = "ml.t2.medium",
    tags = list("my-tag" = "support-vector-machine")
  )
```

## Build Docker container and deploy endpoint (1 big function)):

```{r}
new_endpoint <-
  vetiver_deploy_sagemaker(
    model_board,
    "biv-svm",
    "ml.t2.medium",
    predict_args = list(type = "class", debug = TRUE),
    repo_name = glue::glue("vetiver-sagemaker-{ids::adjective_animal(style = 'kebab')}")
  )
```



## Make a prediction with your deployed model

Wait for the endpoint to finish deploying and then make a prediction like so in the interactive visual documentation under "Deployments" and then "Endpoints":

```
[
  {
    "A": 100,
    "B": 10
  },
  {
    "A": 10,
    "B": 10
  } 
]
```

Get predictions in R:

```{r}
new_biv <- bivariate_test %>% slice_sample(n = 50) 
predict(new_endpoint, new_biv)
```


