---
title: "Using vetiver on SageMaker"
output: html_document
date: '2022-07-19'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Train a model

```{r}
library(tidymodels)
data(bivariate)

biv_rec <-
  recipe(Class ~ ., data = bivariate_train) %>%
  step_BoxCox(all_predictors())%>%
  step_normalize(all_predictors())

svm_spec <-
  svm_linear(mode = "classification") %>%
  set_engine("LiblineaR")

svm_fit <- workflow(biv_rec, svm_spec) %>%
  fit(bivariate_train)

```

## Create a deployable vetiver model

```{r}
library(vetiver)
v <- vetiver_model(svm_fit, "biv-svm")
v

## manually add paws.storage for now
v$metadata$required_pkgs <- c(v$metadata$required_pkgs, "paws.storage")
```

## Publish and version model on AWS S3

```{r}
library(paws)

library(pins)
identifier <- "sagemaker-vetiver-biv-svm"
svc <- s3()
svc$create_bucket(
  Bucket = identifier,
  CreateBucketConfiguration = list(LocationConstraint = "us-east-2")
)

model_board <- board_s3(bucket = identifier)
vetiver_pin_write(model_board, v)
```

To create API app files:

```{r}
vetiver_write_plumber(
  model_board,
  "biv-svm",
  type = "class",
  path = "/invocations",
  debug = TRUE,
  file = "plumber.R"
)
vetiver_write_docker(v, port = 8080)
```

## Build Docker container

In terminal, in directory with Dockerfile (working directory in this demo):

(May need to do `export PATH=/home/sagemaker-user/.local/bin:$PATH` first)

```{bash}
sm-docker build . --repository sagemaker-vetiver-biv-svm:1.0 --bucket sagemaker-vetiver-biv-svm
```

Be sure to notice/record image URI!

## Deploy image as SageMaker model

```{r}
library(reticulate)
library(glue)

sagemaker <- import("sagemaker")
role <- sagemaker$get_execution_role()

## set seed here for reproducible identifier
model_identifier <- glue::glue("vetiver-sagemaker-", ids::adjective_animal(style = "kebab"))
sm_model_name <- model_identifier
endpoint_config <- glue("{model_identifier}-endpoint-config")
```

```{r}
sm <- sagemaker()

## use image URI from building:
sm$create_model(
  ModelName = sm_model_name,
  ExecutionRoleArn = role,
  PrimaryContainer = list(
    Image = "350573666743.dkr.ecr.us-east-2.amazonaws.com/sagemaker-vetiver-biv-svm:1.0"
  )
)

sm$create_endpoint_config(
  EndpointConfigName = endpoint_config, 
  ProductionVariants = list(
    list(
      VariantName = "AllTraffic",
      ModelName = sm_model_name,
      InitialInstanceCount = 1,
      InstanceType = "ml.t2.medium",
      InitialVariantWeight = 1
    )
  )
)

sm$create_endpoint(
  EndpointName = sm_model_name, 
  EndpointConfigName = endpoint_config
)

```


## Make a prediction with your deployed model

Make a prediction like so in the interactive visual documentation:

```
[
  {
    "A": 100,
    "B": 10
  },
  {
    "A": 10,
    "B": 10
  } 
]
```

Get predictions in R:

```{r}
new_biv <- bivariate_test %>% slice_sample(n = 50) %>% jsonlite::toJSON()
sm_runtime <- sagemakerruntime()
preds <- sm_runtime$invoke_endpoint("sagemaker-vetiver-biv-svm", new_biv)

preds_parsed <- rawToChar(preds$Body) %>% jsonlite::fromJSON()
as_tibble(preds_parsed)
```



